---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
ragg_png <- function(..., res = 150) {
  ragg::agg_png(..., res = res, units = "in")
}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "ragg_png"
)
```

# luciole

<!-- badges: start -->
<!-- badges: end -->

Luciole typeface for R projects (Shiny applications, RMarkdown documents, ggplot2 graphics, ...).

From [Luciole official website](https://luciole-vision.com/luciole-en.html):

> Luciole (French for “firefly”) is a new typeface developed explicitly for visually impaired people. The result of a two-year collaboration between the Centre Technique Régional pour la Déficience Visuelle (the Regional Technical Center for Visual Impairment) and the type-design studio typographies.fr, this project received a grant from the Swiss Ceres Foundation and support from the DIPHE laboratory at the Université Lumière Lyon 2.


## Installation

You can install the development version of luciole from [GitHub](https://github.com/dreamRs/luciole) with:

``` r
# install.packages("remotes")
remotes::install_github("dreamRs/luciole")
```

## Examples

### ggplot2

Register Luciole font with:

```{r register_luciole}
luciole::register_luciole()
```


The declare the `"Luciole"` family in your graphics:

```{r ggplot2}
library(ggplot2)
ggplot() +
  aes(0, 0, label = "lisibilité") +
  geom_text(size = 30, family = "Luciole") + 
  theme_grey(base_family = "Luciole")
```


In Rstudio, to use Luciole you have to select the ragg device to render plots, see [this excellent blogpost by June Choe ](https://yjunechoe.github.io/posts/2021-06-24-setting-up-and-debugging-custom-fonts/) for more informations.


### Shiny

For using Luciole with all text rendered in HTML in a shiny application, use in your UI:

```{r luciole_font, eval=FALSE}
luciole_font()
```

Example:

```{r shiny, eval=FALSE}

```

