---
title: "luciole"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{luciole}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/", 
  fig.retina = 1, 
  fig.height = 6, 
  fig.width = 8
)
```

```{r setup}
library(luciole)
```

```{r attach-luciole, include=FALSE}
attach_luciole()
```


## ggplot2

Add Luciole font with:

```{r add_luciole}
add_luciole(showtext_auto = TRUE)
```

It will add Luciole font family to 'sysfonts', and allow its use in graphics through the package [showtext](https://github.com/yixuan/showtext).


Then declare the `"Luciole"` family in your graphics:

```{r ggplot2}
library(ggplot2)
ggplot() +
  aes(0, 0, label = "lisibilité") +
  geom_text(size = 20, family = "Luciole") + 
  theme_grey(base_family = "Luciole")
```


## R Markdown

In a R Markdown document, you can use Luciole with an HTML output. Use a chunk like below in your Rmd:

````
```{r attach-luciole, include=FALSE}`r ''`
attach_luciole()
```
````

Then all text will be rendered using Luciole (like this document). Here's some examples character:

```{r rmarkdown}
tag_example(style = "font-size: 2rem;")
```



## Shiny

Load Luciole CSS & font files into your page with:

```{r luciole_font, eval=FALSE}
luciole_font_dependency()
```

By default a style tag is injected in the head of the page to use Luciole in all the HTML body.

Example:

```{r shiny, eval=FALSE}
library(shiny)

ui <- fluidPage(
  
  luciole_font_dependency(),
  
  tags$h2("Hello, I'm using Luciole font to improve lisibility.")
)

server <- function(input, output, session) {
  
}

shinyApp(ui, server)
```
